% !TEX root = tesi.tex
\begin{thebibliography}{99}
 
\bibitem{popovski}
  Peter Popovski, Frank H.P. Fitzek, Ramjee Prasad, \emph{ A Class of Algorithms for Collision Resolution with Multiplicity Estimation}, Springer, Algorithmica, Vol. 49, No. 4, December 2007, 286-317
  
\bibitem{lucent}
Murali Kodialam, Thyaga Nandagopal, \emph{Fast and Reliable Estimation Schemes in RFID Systems}, MobiCom '06: Proceedings of the 12th annual international conference on Mobile computing and networking, ACM , September 2006, 322-333 
 
\bibitem{sift}
K. Jamieson, H. Balakrishnan, and Y. C. Tay, \emph{Sift: a MAC protocol for event-driven wireless sensor networks},  Proc. 3rd European Workshop on Wireless Sensor Networks, Zurich, Switzerland, February 2006, pp. 260–275 

\bibitem{cidon}
 Israel Cidon, Moshe Side, \emph{Conflict Multiplicity Estimation and Batch Resolution Algorithms}, IEEE Transactions On Information Theory, Vol. 34, No. 1, January 1988, 101-110
 
\bibitem{greenberg87}
  Albert G. Greenberg, Philippe Flajolet,  Richard E. Ladner,
  \emph{Estimating the Multiplicities of Conflicts to Speed Their Resolution in Multiple Access Channels},
  Journal of the Association for Computing Machinery,
  Vol 34, No. 2, April 1987, 289-325
 
 \bibitem{capetanakis}
  J.I. Capetanakis, \emph{ Tree algorithms for packet broadcast channels}, IEEE Transactions On Information Theory, Vol. 25, No. 5, September 1979, 505-515
 
\bibitem{tsybakov}
B. S. Tsybakov, V. A. Mikhailov, \emph{Slotted multiaccess packet broadcasting feedback channel}, Probl. Peredachi Inform. vol. 13, December 1978, 32-59
 
\bibitem{capetanakis77}
J.I. Capetanakis, \emph{A protocol for resolving conflicts on ALOHA channels}, Abstracts of Papers, IEEE Int. Symp. Info. Th., Ithaca, New York, October 1977, 122-123

 \end{thebibliography}
 
